\documentclass[fleqn,twoside,twocolumn,nofootinbib,showkeys]{revtex4} % Specifies the document class %,unsortedaddress
%\usepackage[sec]{ujp} % \usepackage[cyr]{ujp} for cyrillic
\usepackage[sec,doi]{ujp_UTF8} % \usepackage[cyr]{ujp_UTF8} for cyrillic

\usepackage{orcidlink} % to insert a hyperlinked ORCiD logo
\usepackage{amssymb}
\usepackage{physics}
%\usepackage{cite} % may be useful for different formats of numerical citation
\usepackage{hyperref} % for hyperlinks in references
\usepackage[nameinlink]{cleveref}
\usepackage{caption} % for \caption*
\usepackage{amsmath}    % for "\eqref" macro
\usepackage{graphicx}

\begin{document}
	\title[Thermodynamic response functions in a cell fluid model]%колонтитул
	{THERMODYNAMIC RESPONSE FUNCTIONS IN A CELL FLUID MODEL}%
	\author{O.A.~Dobush}%1
	\author{M.P.~Kozlovskii}
	\author{R.V.~Romanik}
	\author{I.V.~Pylyuk}
	\affiliation{Institute for Condensed Matter Physics,\\ Nat. Acad. of Sci. of Ukraine}%інститут 1
	\address{1, Svientsitskii Str., Lviv 79011, Ukraine}%адреса 1
	\email{dobush@icmp.lviv.ua}%e-mail 1
	\email{mpk@icmp.lviv.ua}
	\email{romanik@icmp.lviv.ua}
	\email{piv@icmp.lviv.ua}
	
	\udk{№ УДК/UDC} \razd{\secv}
	
	\autorcol{O.A.\hspace*{0.7mm}Dobush, M.P.\hspace*{0.7mm}Kozlovskii, R.V.\hspace*{0.7mm}Romanik, I.V.\hspace*{0.7mm}Pylyuk}%
	
	\setcounter{page}{1}%
	
	\begin{abstract}
		Thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient, are calculated for a many-particle system interacting through a modified Morse potential. These calculations are based on an equation of state previously derived for a cell fluid model in the grand canonical ensemble. The calculated quantities are presented graphically as functions of density and chemical potential.
	\end{abstract}
	
	\keywords{Cell model, Morse potential, Thermodynamic response functions}
	
	\maketitle
	
	\input{./paper_text.tex}
	
	\vskip3mm \textit{Acknowledgement.}
	
	\bibliography{extracted}
		
	\vspace*{-5mm}\rezume{%Резюме укр. мовою
		О.А.~Добуш, М.П.~Козловський, Р.В.~Романік, І.В.~Пилюк}{ТЕРМОДИНАМІЧНІ ФУНКЦІЇ ВІДГУКУ КОМІРКОВОЇ МОДЕЛІ} {Текст резюме укр. мовою.}{\textit{К\,л\,ю\,ч\,о\,в\,і\,
			с\,л\,о\,в\,а:} коміркова модель, потенціал Морзе, термодинамічні функції відгуку.}
	
\end{document}
